Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
phrs

Yet, so far, EHRs have primarily been limited to the storage of
official diagnostic reports prepared by clinicians, technicians and
nurses.  These communications are both highly technical, making them
difficult to interpret by end-user patients, but also highly limited
in temporal resolution, reflecting only cases where a person was
attended to and diagnostic-tested by a medical professional.  Although
this may be frequent for patients in inpatient care, those that come
to see their clinician, say, once a month end up with extremely
low-resolution views of a patient's condition.

>>>>

Yet, so far, EHRs have primarily been limited to the storage of
official diagnostic reports prepared by clinicians, technicians and
nurses.  These communications are both highly technical, making them
difficult to interpret by end-user patients, but also highly limited
in temporal resolution, reflecting only cases where a person was
attended to and diagnostic-tested by a medical professional.  Although
this may be frequent for patients in inpatient care, those that come
to see their clinician, say, once a month end up with extremely
low-resolution samples of a patient's condition.
